Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-20 papers/paper-eccentricity/paper-eccentricity.tex
First version of Intro done

In this Letter, based on simulations run with the KETJU code \citep{mannerkoski2023}, we find that the SMBH binary eccentricity is reliably predictable only for particular
initial conditions of the galaxy merger system, and does not in general hold.
Indeed, we find that for realistic galaxy merger orbits \citep{khochfar2006} where the initial orbital eccentricity of the system is $e_0>0.90$, stochasticity in the final
SMBH binary eccentricity is always present.

>>>>

In this Letter, based on simulations run with the KETJU code, we find that the SMBH binary eccentricity is reliably predictable only for particular
initial conditions of the galaxy merger system, and does not in general hold.
Indeed, we find that for realistic galaxy merger orbits where the initial orbital eccentricity of the system is $e_0>0.90$, stochasticity in the final
SMBH binary eccentricity is always present.
